---
title: 'Bybit Seasonality Analysis'
author: 'Ravi Brock'
date: '10/13/2022'
output: 'Table'
purpose: 'Calculates average change by time on Bybit perps'
---

# Installs and loads libraries
```{r}
# install.packages('jsonlite')
# install.packages('gt')
# install.packages('tidyverse')
library(jsonlite)
library(gt)
library(tidyverse)
```

# Parameters
```{r}
period <- 168 # Length in hours to analyze seasonality over
granularity <- 'D' # How detailed should the interperiod price change be
lookback <- 8 # How many periods should be analyzed

options(scipen = 100)
```

# Functions to transform data and pull from the API
```{r}
bybitdata <- function(link) {
  contents <- httr::RETRY('GET', 
    url = link, 
    config = list(), 
    body = NULL, 
    encode = c("json"), 
    times = 3, 
    pause_base = 1, 
    pause_cap = 60, 
    pause_min = 1, 
    handle = NULL, 
    quiet = FALSE, 
    terminate_on = NULL, 
    terminate_on_success = TRUE
    )
    
  if(httr::http_status(contents)$category == 'Success') {
    contents <- httr::content(contents,
      as = NULL,
      type = NULL,
      encoding = NULL
    )
    contents <- as.data.frame(contents)
  }
  
  return(contents)
}
  
flat_to_df <- function(start_df, final_df, start_column, end_offset) {
  loop_row <- 1
  col_number <- NCOL(final_df)
  max_cell <- NCOL(start_df) - end_offset
  
  while (start_column + col_number - 1 <= max_cell) {
    final_df[loop_row,] <- start_df[1, start_column:(start_column + (col_number - 1))]
    start_column <- start_column + col_number
    loop_row <- loop_row + 1
  }
  
  return(final_df)
}
```

# Sets start time and subdivisions of periods
```{r}
starttime <- floor(as.numeric(as.POSIXct(Sys.time()))) - lookback * period * 3600

if (granularity == "D") {
  granularity2 <- 24
} else if (granularity == "W") {
  granularity2 <- 168
} else {
  granularity2 <- granularity
}
```

# Pulls and processes list of tickers
```{r}
tickers <- fromJSON('https://api.bybit.com/v2/public/symbols') %>%
  as.data.frame
tickers <- filter(tickers, tickers$'result.quote_currency' == 'USDT') # Filters out inverse perpetuals
tickers_orgnl <- tickers
tickers = tickers[-1,]
row.names(tickers) <- 1:nrow(tickers)
tickers <- tickers$'result.name'
tickers_orgnl <- tickers_orgnl$'result.name'
ticker_count <- length(tickers)
```

# Pulls OHLC data for BTC and calculates per-candle deviation from VWAP
```{r}
# Retry logic to pull data from Bybit API
rawdata <- bybitdata(paste('https://api.bybit.com/public/linear/kline?symbol=BTCUSDT&interval=', granularity, '&from=', starttime, sep='', collapse=NULL))

# Rearranges Bybit API data into dataframe
btc <- data.frame('id', 'symbol', 'period', 'interval', 'starttime', 'opentime', 'volume', 'open', 'high', 'low', 'close', 'turnover')
btc <- flat_to_df(rawdata, btc, 5, 1)
btc <- suppressWarnings(mutate_all(btc, function(x) as.numeric(as.character(x))))
btc <- subset(btc, select = -c(1:6))
```

# Pulls data, writes to a 3-dimensional array with all alt price dataframes
```{r}
# Pull data for each ticker, write to an array
current_ticker <- 1
max.ticker <- NROW(tickers)
perpdata <- data.frame(Ticker = c(NA))

# Initializes 3D array with the same row count as btc df, 7 columns, and the same height as {ticker count - 1} since BTCUSDT is skipped
alts <- array(unlist(rep(btc, NROW(tickers))), dim=c(NROW(btc), 6, NROW(tickers) + 1))

while (current_ticker <= max.ticker) {
  # Retry logic to pull data from Bybit API
  rawdata <- bybitdata(paste('https://api.bybit.com/public/linear/kline?symbol=', tickers[current_ticker], '&interval=', granularity, '&from=', starttime, sep='', collapse=NULL))

  # Rearranges Bybit API data into dataframe
  alt <- data.frame('id', 'symbol', 'period', 'interval', 'starttime', 'opentime', 'volume', 'open', 'high', 'low', 'close', 'turnover')
  alt <- flat_to_df(rawdata, alt, 5, 1)
  alt <- suppressWarnings(mutate_all(alt, function(x) as.numeric(as.character(x))))
  alt <- subset(alt, select = -c(1:6))
  if (NROW(alt) < 56) {
    alt[(NROW(alt) + 1):56, 1:6] <- 0
  }
  alt <- data.matrix(alt)
  alts[,, current_ticker + 1] <- alt
  current_ticker <- current_ticker + 1
}
```

# Creates new df with standard deviations per alt organized by (subset, period)
```{r}
max_row <- NROW(btc)
current_ticker <- 1

while (current_ticker <= ticker_count) {
  alt <- alts[,,current_ticker]
  alt <- as.data.frame(alt)
  
  current_row <- 1
  while (current_row <= max_row) {
    if (alt[current_row, 1] != 0) {
      alt[current_row, 6] <- (alt[current_row, 5]  - alt[current_row, 2]) / alt[current_row, 2]
    }
    current_row <- current_row + 1
  }
  
  alt2 <- as.data.frame(matrix(nrow = 1, ncol = period / granularity2))
  pct_change <- as.data.frame(t(alt[,6]))
  alt2 <- flat_to_df(pct_change, alt2, 0, 0)
  alt2 <- data.matrix(alt2)
  alt2 <- (alt2-mean(alt2, na.rm = TRUE))/sd(alt2, na.rm = TRUE)
  
  if (current_ticker == 1) {
    alts2 <- array(unlist(rep(alt2, NROW(tickers) + 1)), dim=c(NROW(alt2), NCOL(alt2), NROW(tickers) + 1))
  }
  
  alts2[,,current_ticker] <- alt2
  current_ticker <- current_ticker + 1
}
```

# Flattens dataframes by writing average by period into final table with 1 row per alt
```{r}
max_ticker <- ticker_count + 1
current_ticker <- 1
final_alt <- as.data.frame(matrix(nrow = 1, ncol = period / granularity2))

while (current_ticker <= max_ticker) {
  alt <- alts2[,,current_ticker]
  alt <- as.data.frame(alt)
  
  max_col <- NCOL(alt)
  start_col <- 1
  
  while (start_col <= max_col) {
    final_alt[current_ticker, start_col] <- mean(alt[,start_col], na.rm = TRUE)
    start_col <- start_col + 1
  }
  
  current_ticker <- current_ticker + 1
}
```

#Adjusts for Bitcoin seasonality
```{r}
adjusted_seasonality <- final_alt

max_col <- NCOL(adjusted_seasonality)
start_col <- 1

while (start_col <= max_col) {
  adjusted_seasonality[,start_col] <- adjusted_seasonality[,start_col] - adjusted_seasonality[1,start_col]
  start_col <- start_col + 1
}
```

# Renames columns, rounds everything to 2 decimal points, and displays final results
```{r}
final_alt <- cbind(tickers_orgnl, final_alt)
final_alt <- final_alt %>%
  mutate_if(is.numeric, round, digits = 2)
final_alt$tickers_orgnl <- gsub('USDT', '', final_alt$tickers_orgnl)
final_alt <- final_alt

adjusted_seasonality <- cbind(tickers_orgnl, adjusted_seasonality)
adjusted_seasonality <- adjusted_seasonality %>%
  mutate_if(is.numeric, round, digits = 2)
adjusted_seasonality$tickers_orgnl <- gsub('USDT', '', adjusted_seasonality$tickers_orgnl)

colnames(final_alt)[1] <- "Ticker"
colnames(adjusted_seasonality)[1] <- "Ticker"

view(final_alt)
view(adjusted_seasonality)
```
