---
title: 'Bybit Perpetual Futures Screener'
author: 'Ravi Brock'
date: '5/20/2022'
output: 'Table'
purpose: 'Provides a number of statistics for Bybit perps over a given period of time'
---

# Installs and loads libraries
```{r}
# install.packages('jsonlite')
# install.packages('gt')
# install.packages('tidyverse')
library(jsonlite)
library(gt)
library(tidyverse)
```

# Parameters
```{r}
timeframe <- 24 # Timeframe in hours
change <- TRUE
funding <- TRUE
longshort_ratio <- TRUE
beta <- TRUE
strength <- TRUE
speculative_index <- FALSE

options(scipen = 100)
```

# Functions to transform data and pull from the API
```{r}
bybitdata <- function(link) {
  contents <- httr::RETRY('GET', 
    url = link, 
    config = list(), 
    body = NULL, 
    encode = c("json"), 
    times = 3, 
    pause_base = 1, 
    pause_cap = 60, 
    pause_min = 1, 
    handle = NULL, 
    quiet = FALSE, 
    terminate_on = NULL, 
    terminate_on_success = TRUE
    )
    
  if(httr::http_status(contents)$category == 'Success') {
    contents <- httr::content(contents,
      as = NULL,
      type = NULL,
      encoding = NULL
    )
    contents <- as.data.frame(contents)
  }
  
  return(contents)
}
  
flat.to.df <- function(startdf, finaldf, startcolumn, endoffset) {
  loop.row <- 1
  colnumber <- NCOL(finaldf)
  maxcell <- NCOL(startdf) - endoffset
  
  while(startcolumn + colnumber - 1 <= maxcell) {
    finaldf[loop.row,] <- startdf[1, startcolumn:(startcolumn + (colnumber - 1))]
    startcolumn <- startcolumn + colnumber
    loop.row <- loop.row + 1
  }
  
  return(finaldf)
}
```

# Converts candlelength to seconds, sets start + end time, and validates candle length
```{r}
candlelength <- round((timeframe * 60 / 200), digits = 0)

if(candlelength < 1) {
  candlelength <- 1
} else if(1 < candlelength & candlelength < 3) {
  candlelength <- 3
} else if(2 < candlelength & candlelength < 5) {
  candlelength <- 5
} else if(5 < candlelength & candlelength < 15) {
  candlelength <- 15
} else if(15 < candlelength & candlelength < 30) {
  candlelength <- 30
} else if(30 < candlelength & candlelength < 60) {
  candlelength <- 60
} else if(60 < candlelength & candlelength < 120) {
  candlelength <- 120
} else if(120 < candlelength & candlelength < 240) {
  candlelength <- 240
} else if(240 < candlelength & candlelength < 360) {
  candlelength <- 360
} else if(360 < candlelength & candlelength < 720) {
  candlelength <- 720
} else if(720 < candlelength & candlelength < 1440) {
  candlelength <- 'D'
} else if(1440 < candlelength & candlelength < 10040) {
  candlelength <- 'W'
} else if(10080 < candlelength) {
  print('Timeframe too long.')
}

starttime <- floor(as.numeric(as.POSIXct(Sys.time()))) - timeframe * 3600
```

# Pulls and processes list of tickers
```{r}
tickers <- fromJSON('https://api.bybit.com/v2/public/symbols') %>%
  as.data.frame
tickers <- filter(tickers, tickers$'result.quote_currency' == 'USDT') # Filters out inverse perpetuals
tickers = tickers[-1,]
rownames(tickers) <- 1:nrow(tickers)
tickers <- tickers$'result.name'
```

# Pulls OHLC data for BTC and calculates per-candle deviation from VWAP
```{r}
# Retry logic to pull data from Bybit API
rawdata <- bybitdata(paste('https://api.bybit.com/public/linear/kline?symbol=BTCUSDT&interval=', candlelength, '&from=', starttime, sep='', collapse=NULL))

# Rearranges Bybit API data into dataframe
btc <- data.frame('id', 'symbol', 'period', 'interval', 'starttime', 'opentime', 'volume', 'open', 'high', 'low', 'close', 'turnover')
btc <- flat.to.df(rawdata, btc, 5, 1)
btc <- suppressWarnings(mutate_all(btc, function(x) as.numeric(as.character(x))))
btc <- subset(btc, select = -c(1:6))

# Calculates deviation from the VWAP as a percentage for each candle
currentrow <- 1
maxrow <- NROW(btc)

while(currentrow <= maxrow) {
  btc[currentrow, 6] <- (btc[currentrow, 3] + btc[currentrow, 4] + btc[currentrow, 5])/3 * btc[currentrow, 1]
  currentrow <- currentrow + 1
}
vwap.btc <- sum(btc$X.turnover.)/sum(btc$X.volume.)
currentrow <- 1

while(currentrow <= maxrow) {
  btc[currentrow, 6] <- (((btc[currentrow, 3] + btc[currentrow, 4] + btc[currentrow, 5]) / 3) - vwap.btc)/vwap.btc
  btc[currentrow, 'variancebase'] <- btc[currentrow, 6] ^ 2
  currentrow <- currentrow + 1
}
variance.btc <- mean(btc$variancebase)
```

# Pulls data, writes to a 3-dimensional array with all alt price dataframes
```{r}
# Pull data for each ticker, write to an array
current.ticker <- 1
max.ticker <- NROW(tickers)
perpdata <- data.frame(Ticker = c(NA))

# Initializes 3D array with the same row count as btc df, 7 columns, and the same height as {ticker count - 1} since BTCUSDT is skipped
alts <- array(unlist(rep(btc, NROW(tickers))), dim=c(NROW(btc), 7, NROW(tickers)))

while(current.ticker <= max.ticker) {
  # Retry logic to pull data from Bybit API
  rawdata <- bybitdata(paste('https://api.bybit.com/public/linear/kline?symbol=', tickers[current.ticker], '&interval=', candlelength, '&from=', starttime, sep='', collapse=NULL))

  # Rearranges Bybit API data into dataframe
  alt <- data.frame('id', 'symbol', 'period', 'interval', 'starttime', 'opentime', 'volume', 'open', 'high', 'low', 'close', 'turnover')
  alt <- flat.to.df(rawdata, alt, 5, 1)
  alt <- suppressWarnings(mutate_all(alt, function(x) as.numeric(as.character(x))))
  alt <- subset(alt, select = -c(1:6))

  alt[1:96, 7] <- btc$variancebase
  alt <- data.matrix(alt, rownames.force = NA)
  alt <- alt[1:NROW(btc),]
  alts[,,current.ticker] <- alt
  perpdata[current.ticker,] <- tickers[current.ticker]
  current.ticker <- current.ticker + 1
}

tickercount <- NROW(tickers)
```

# Calculates 24 hour % change per alt
```{r}
if(change == TRUE) {
  maxrow <- NROW(btc)
  current.ticker <- 1
  
  Change <- rep(NA, tickercount)
  perpdata <- cbind(perpdata, Change)
  perpdata <- as.data.frame(perpdata)
  perpdata$Change <- as.numeric(as.character(perpdata$Change))
  
  while(current.ticker <= tickercount) {
    alt <- alts[,,current.ticker]
    alt <- as.data.frame(alt)
    
    perpdata[current.ticker, 'Change'] <- (alt[maxrow, 5] - alt[1, 2]) / alt[1, 2] * 100
    current.ticker <- current.ticker + 1
  }
  names(perpdata)[NCOL(perpdata)] <- 'Change (%)'
}
```

# Calculates each alt's annualized funding rate
```{r}
if(funding == TRUE) {
  maxrow <- NROW(btc)
  current.ticker <- 1
  
  Funding <- rep(NA, tickercount)
  perpdata <- cbind(perpdata, Funding)
  perpdata <- as.data.frame(perpdata)
  perpdata$Funding <- as.numeric(as.character(perpdata$Funding))
  
  while(current.ticker <= tickercount) {
    fundingrate <- httr::RETRY('GET', 
    url = paste('https://api.bybit.com/public/linear/funding/prev-funding-rate?symbol=', tickers[current.ticker], sep='', collapse=NULL), 
    config = list(), 
    body = NULL, 
    encode = c("json"), 
    times = 3, 
    pause_base = 1, 
    pause_cap = 60, 
    pause_min = 1, 
    handle = NULL, 
    quiet = FALSE, 
    terminate_on = NULL, 
    terminate_on_success = TRUE
    )
    
    if(httr::http_status(fundingrate)$category == 'Success') {
    fundingrate <- httr::content(fundingrate, 
      as = NULL, 
      type = NULL,
      encoding = NULL
      )
    }
    
    fundingrate <- fundingrate$result$funding_rate
    
    perpdata[current.ticker, 'Funding'] <- fundingrate * 109500
    current.ticker <- current.ticker + 1
  }
  names(perpdata)[NCOL(perpdata)] <- 'Annualized Funding (%)'
}
```

# Long-short ratio
```{r}
if(longshort_ratio == TRUE) {
  maxrow <- NROW(btc)
  current.ticker <- 1
  
  LSratio <- rep(NA, tickercount)
  perpdata <- cbind(perpdata, LSratio)
  perpdata <- as.data.frame(perpdata)
  perpdata$LSratio <- as.numeric(as.character(perpdata$LSratio))
  
  while(current.ticker <= tickercount) {
    rawdata <- bybitdata(paste('https://api.bybit.com//v2/public/account-ratio?symbol=', tickers[current.ticker], '&period=5min', sep='', collapse=NULL))

    ratio <- data.frame('symbol', 'buyratio', 'sellratio', 'timestamp')
    ratio <- flat.to.df(rawdata, ratio, 5, 1)
    ratio <- suppressWarnings(mutate_all(ratio, function(x) as.numeric(as.character(x))))
    
    perpdata[current.ticker, 'LSratio'] <- (ratio[1, 4] - ratio[1, 1]) * 100
    current.ticker <- current.ticker + 1
  }
  names(perpdata)[NCOL(perpdata)] <- 'Long-Short Δ'
}
```

# Calculates beta for each candle and outputs into final dataframe
```{r}
if(beta == TRUE) {
  maxrow <- NROW(btc)
  current.ticker <- 1
  
  Beta <- rep(NA, tickercount)
  perpdata <- cbind(perpdata, Beta)
  perpdata <- as.data.frame(perpdata)
  perpdata$Beta <- as.numeric(as.character(perpdata$Beta))
  
  while(current.ticker <= tickercount) {
    currentrow <- 1
    
    alt <- alts[,,current.ticker]
    alt <- as.data.frame(alt)
    
    while(currentrow <= maxrow) {
        alt[currentrow, 7] <- (alt[currentrow, 3] + alt[currentrow, 4] + alt[currentrow, 5])/3 * alt[currentrow, 6]
        currentrow <- currentrow + 1
    }
    vwap.alt <- sum(alt$V7)/sum(alt$V6)
    currentrow <- 1
      
    while(currentrow <= maxrow) {
      alt[currentrow, 7] <- (vwap.alt - (alt[currentrow, 3] + alt[currentrow, 4] + alt[currentrow, 5])/3)/vwap.alt
      currentrow <- currentrow + 1
    }
    currentrow <- 1
    
    # Creates dataframe holding BTC deviation, ALT deviation, and BTC deviation * ALT deviation
    btcalt <- data.frame('btc', 'alt', 'btc x alt')
    while(currentrow <= maxrow) {
      btcalt[currentrow, 'btc'] <- btc[currentrow, 7]
      btcalt[currentrow, 'alt'] <- alt[currentrow, 7]
      btcalt[currentrow, 'btc x alt'] <- btcalt[currentrow, 'btc'] * btcalt[currentrow, 'alt']
      currentrow <- currentrow + 1
    }
    btcalt <- select(btcalt, (NCOL(btcalt) - 2):(NCOL(btcalt)))
    btcalt <- suppressWarnings(mutate_all(btcalt, function(x) as.numeric(as.character(x))))
    
    # Creates dataframe holding each alt and it's beta
    perpdata[current.ticker, 'Beta'] <- (sum(btcalt$'btc x alt') / maxrow) / variance.btc * 100
    
    current.ticker <- current.ticker + 1
  }
}
```

# Calculates strength of each alt
```{r}
if (strength == TRUE) {
  maxrow <- NROW(btc)
  current.ticker <- 1
  
  Strength <- rep(NA, tickercount)
  perpdata <- cbind(perpdata, Strength)
  perpdata <- as.data.frame(perpdata)
  perpdata$Strength <- as.numeric(as.character(perpdata$Strength))
  
  while(current.ticker <= tickercount) {
    currentrow <- 1
    
    alt <- alts[,,current.ticker]
    alt <- as.data.frame(alt)
    
    strength.up <- 0
    count.up <- 0
    strength.down <- 0
    count.down <- 0
    
    while(currentrow <= maxrow) {
      open.alt <- alt[currentrow, 2]
      close.alt <- alt[currentrow, 5]
      open.btc <- btc[currentrow, 2]
      close.btc <- btc[currentrow, 5]
      
      if(close.btc > open.btc) {
        strength.up <- strength.up + ((close.alt - open.alt) / open.alt - (close.btc - open.btc) / open.btc)
        count.up <- count.up + 1
      } else if(close.btc < open.btc) {
        strength.down <- strength.down + ((close.alt - open.alt) / open.alt - (close.btc - open.btc) / open.btc)
        count.down <- count.down + 1
      }
      
      currentrow <- currentrow + 1
    }
    
    perpdata[current.ticker, 'Strength'] <- (strength.up / count.up + strength.down / count.down) * (2500)
    current.ticker <- current.ticker + 1
  }
}
```

# Calculates "Speculation Index"
```{r}
if(speculative_index == TRUE) {
  maxrow <- NROW(btc)
  current.ticker <- 1
  
  Speculation <- rep(NA, tickercount)
  perpdata <- cbind(perpdata, Speculation)
  perpdata <- as.data.frame(perpdata)
  perpdata$Speculation <- as.numeric(as.character(perpdata$Speculation))
  
  while(current.ticker <= tickercount) {
    rawdata <- bybitdata(paste('https://api.bybit.com/v2/public/open-interest?symbol=', tickers[current.ticker], '&period=1h', '&limit=', timeframe, sep='', collapse=NULL))
    
    openinterest <- data.frame('OI', 'timestamp', 'symbol')
    openinterest <- flat.to.df(rawdata, openinterest, 5, 1)
    openinterest <- suppressWarnings(mutate_all(openinterest, function(x) as.numeric(as.character(x))))
    
    oi <- openinterest[1, 1]
    oidelta <- openinterest[1, 1] - openinterest[timeframe, 1]
    
    perpdata[current.ticker, 'Speculation'] <- sum(alt$V1) / oi
    current.ticker <- current.ticker + 1
  }
  names(perpdata)[NCOL(perpdata)] <- 'Speculative Index'
}
```

# Renames columns in perpdata, rounds everything to 2 decimal points, and displays final results
```{r}
perpdata <- perpdata %>%
  mutate_if(is.numeric, round, digits = 2)
perpdata$Ticker <- gsub('USDT', '', perpdata$Ticker)

view(perpdata)
```
