---
title: 'Bybit Perpetual Futures Screener'
author: 'Ravi Brock'
date: '4/18/2023'
output: pdf_document
purpose: 'Charts regular and log returns for all Bybit alts'
---

# Installs and loads libraries
```{r}
# install.packages('jsonlite')
# install.packages('directlabels')
# install.packages('gt')
# install.packages("reshape")
# install.packages
library(directlabels)
library(jsonlite)
library(gt)
library(reshape)
library(tidyverse)
```

# Parameters
```{r}
start_time <- 1681858800 # Start time (unix timestamp)
data_source <- "CLOSE" # OPEN, HIGH, LOW, or CLOSE

options(scipen = 100)
```

# Functions to transform data and pull from the API
```{r}
bybitdata <- function(link) {
  contents <- httr::RETRY('GET', 
    url = link, 
    config = list(), 
    body = NULL, 
    encode = c("json"), 
    times = 3, 
    pause_base = 1, 
    pause_cap = 60, 
    pause_min = 1, 
    handle = NULL, 
    quiet = FALSE, 
    terminate_on = NULL, 
    terminate_on_success = TRUE
    )
    
  if(httr::http_status(contents)$category == 'Success') {
    contents <- httr::content(contents, 
      as = NULL, 
      type = NULL, 
      encoding = NULL
    )
    contents <- as.data.frame(contents)
  }
  
  return(contents)
}
  
flat.to.df <- function(startdf, finaldf, startcolumn, endoffset) {
  lp.row <- 1
  colnumber <- NCOL(finaldf)
  maxcell <- NCOL(startdf) - endoffset
  
  while(startcolumn + colnumber - 1 <= maxcell) {
    finaldf[lp.row, ] <- startdf[1, startcolumn:(startcolumn + (colnumber - 1))]
    startcolumn <- startcolumn + colnumber
    lp.row <- lp.row + 1
  }
  
  return(finaldf)
}
```

# Sets candlelength
```{r}
candlelength <- (as.numeric(Sys.time()) - start_time)/12000

if(candlelength < 1) {
  candlelength <- 1
} else if(1 < candlelength & candlelength < 3) {
  candlelength <- 3
} else if(2 < candlelength & candlelength < 5) {
  candlelength <- 5
} else if(5 < candlelength & candlelength < 15) {
  candlelength <- 15
} else if(15 < candlelength & candlelength < 30) {
  candlelength <- 30
} else if(30 < candlelength & candlelength < 60) {
  candlelength <- 60
} else if(60 < candlelength & candlelength < 120) {
  candlelength <- 120
} else if(120 < candlelength & candlelength < 240) {
  candlelength <- 240
} else if(240 < candlelength & candlelength < 360) {
  candlelength <- 360
} else if(360 < candlelength & candlelength < 720) {
  candlelength <- 720
} else if(720 < candlelength & candlelength < 1440) {
  candlelength <- 'D'
} else if(1440 < candlelength & candlelength < 10040) {
  candlelength <- 'W'
} else if(10080 < candlelength) {
  stop("Timeframe too long.")
}
```

# Transforms data source into column number
```{r}
if(data_source == "OPEN") {
  data_source <- 2
} else if (data_source == "HIGH") {
  data_source <- 3
} else if (data_source == "LOW") {
  data_source <- 4
} else if (data_source == "CLOSE") {
  data_source <- 5
} else {
  stop("Incorrect value for `data_source`.")
}
```

# Pulls and processes list of tickers
```{r}
tickers_original <- fromJSON('https://api.bybit.com/v2/public/symbols') %>%
  as.data.frame
tickers_original <- filter(tickers_original,
                           tickers_original$'result.quote_currency' == 'USDT')
tickers <- filter(tickers_original,
                  tickers_original$'result.name' != 'BTCUSDT')
tickers <- tickers$'result.name'
```

# Pulls OHLC data for BTC and calculates per-candle deviation from VWAP
```{r}
# Retry logic to pull data from Bybit API
url <- paste('https://api.bybit.com/public/linear/kline?symbol=',
             'BTCUSDT',
             '&interval=',
             candlelength,
             '&from=',
             start_time,
             sep='',
             collapse=NULL)
rawdata <- bybitdata(url)

# Rearranges Bybit API data into dataframe
btc <- data.frame('id',
                  'symbol',
                  'period',
                  'interval',
                  'start_time',
                  'opentime',
                  'volume',
                  'open',
                  'high',
                  'low',
                  'close',
                  'turnover')
btc <- flat.to.df(rawdata, btc, 5, 1)
numeric <- function(x) as.numeric(as.character(x))
btc <- suppressWarnings(mutate_all(btc, numeric))
btc <- subset(btc, select = c(6:10))
```

# Pulls data, writes to a 3-dimensional array with all alt price dataframes
```{r}
# Pull data for each ticker, write to an array
current.ticker <- 1
max.ticker <- NROW(tickers)
perpdata <- data.frame(Ticker = c(NA))

# Initializes 3D array
alts <- array(unlist(rep(btc,
                         NROW(tickers))),
                         dim=c(NROW(btc),
                         5,
                         NROW(tickers)+1))
alts[, , 1] <- data.matrix(btc, rownames.force = NA)

while(current.ticker <= max.ticker) {
  # Retry logic to pull data from Bybit API
  url <- paste('https://api.bybit.com/public/linear/kline?symbol=',
               tickers[current.ticker],
               '&interval=',
               candlelength,
               '&from=',
               start_time,
               sep='',
               collapse=NULL)
  rawdata <- bybitdata(url)

  # Rearranges Bybit API data into dataframe
  alt <- data.frame('id',
                    'symbol',
                    'period',
                    'interval',
                    'start_time',
                    'opentime',
                    'open',
                    'high',
                    'low',
                    'close',
                    'volume',
                    'turnover')
  alt <- flat.to.df(rawdata, alt, 5, 1)
  alt <- suppressWarnings(mutate_all(alt, numeric))
  alt <- subset(alt, select = c(6:10))

  # Converts to matrix and adds to next row
  alt <- data.matrix(alt, rownames.force = NA)
  alt <- alt[1:NROW(btc), ]
  alts[, , current.ticker+1] <- alt
  perpdata[current.ticker, ] <- tickers[current.ticker]
  current.ticker <- current.ticker + 1
}

tickercount <- NROW(tickers)
```

# Isolates the time series from the given data source into dataframe
```{r}
alts_df <- data.frame(matrix(nrow=NROW(btc), ncol=NROW(tickers)+1))

i = 1
while (i <= NROW(tickers) + 1) {
  alts_df[, i] <- alts[, data_source, i]
  i <- i + 1
}

alts_df <- cbind(btc[, 1], alts_df)
colnames(alts_df) <- c('timestamp', 'BTCUSDT', tickers)

pct_change <- function(x) ((x - x[1]) / x[1] * 100)
alts_pct <- alts_df
alts_pct[, -1] <- mutate_all(alts_df[, -1], pct_change)
alts_pct[1, -1] <- 0
```

# Plots everything
```{r fig.align="center", fig.width = 25}
alts_melt <- melt(alts_pct[, 1:90], id = "timestamp")
alts_melt$timestamp <- as.POSIXct(alts_melt$timestamp, origin = "1970-01-01")
colnames(alts_melt) <- c("time", "variable", "pct_change")

ggplot(data = alts_melt, aes(x = time, y = pct_change, color = variable)) +
  geom_line() +
  scale_color_discrete(guide = 'none') +
  geom_dl(aes(label = variable), method = list(dl.combine("last.points")))
```
